 \documentclass[11pt, oneside]{book}
\usepackage{setspace}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
%\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage[margin=1.1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{calc}
\usepackage{dsfont}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{multicol}
\usepackage{mathtools,xparse}
\usepackage[hidelinks]{hyperref}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{calligra}

% % % % REFERENCES
%
\usepackage[numbers]{natbib}
\usepackage{amsmath}
%
% % % %

% % % %
%
\usepackage[labelfont=bf]{caption} %labelfont is to make the Figure X.X: in bold
\usepackage[titletoc,toc,page]{appendix}
%
% % % %

% % % % TableFootnote
%
\newcommand*{\savedfootnotes}{}
\newcommand*{\resetsavedfootnotes}{\global\let\savedfootnotes\empty}
\newcommand{\tablefootnote}[1]
{
	\footnotemark
	\xdef\savedfootnotes
	{\unexpanded\expandafter{\savedfootnotes}\noexpand\footnotetext{#1}}
}
\edef\endtable
{
	\aftergroup\noexpand\savedfootnotes
	\aftergroup\noexpand\resetsavedfootnotes
	\unexpanded\expandafter{\endtable}
}
%
% % % %

% % % % Norms
%
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\NewDocumentCommand{\normL}{ s O{} m }{
	\IfBooleanTF{#1}{\norm*{#3}}{\norm[#2]{#3}}_{L_2(\Omega)}%
}
%
% % % %

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\newcommand\phantomarrow[2]{
	\setbox0=\hbox{$\displaystyle #1\to$}
	\hbox to \wd0{
		$#2\mapstochar
		\cleaders\hbox{$\mkern-1mu\relbar\mkern-3mu$}\hfill
		\mkern-7mu\rightarrow$}
	\,}

\graphicspath{{Images//},{sections//},{Images/qualitative_tests/}}
\input epsf

\subfigtopskip=0pt
\subfigcapskip=0pt
\subfigbottomskip=0pt


% % % Sections 
\usepackage{titlesec}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\thechapter}{15pt}{\Huge\bfseries}
%\titlespacing{\chapter}{0pt}{-50pt}{20pt}


%Bigger elements in matrix
\makeatletter
\renewcommand*\env@matrix[1][\arraystretch]{%
	\edef\arraystretch{#1}%
	\hskip -\arraycolsep
	\let\@ifnextchar\new@ifnextchar
	\array{*\c@MaxMatrixCols c}}
\makeatother

% % DEFINITIONS, propositions enviornment
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
% % 


% ALGORITHMS
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{pifont}
%\algdisablelines



\newcommand{\old}{\texttt{algorithmic}}
\newcommand{\euk}{Euclid}
\newcommand\ASTART{\bigskip\noindent\begin{minipage}[b]{0.5\linewidth}}
	\newcommand\ACONTINUE{\end{minipage}\begin{minipage}[b]{0.5\linewidth}}
	\newcommand\AENDSKIP{\end{minipage}\bigskip}
\newcommand\AEND{\end{minipage}}
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmicbreak}{\textbf{break}}

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%
% % % % % % % % % % % % % % % % % % % %

\begin{document}

%\title{Cage active contours: Extension to color spaces and
%		 application to image morphing }
%
%\keywords{The paper must have at least one keyword. The text must be set to 9-point font size and without the use of bold or italic font style. For more than one keyword, please use a comma as a separator. Keywords must be titlecased.}
%
%\abstract{This master thesis explores. experimental results confirm the superiority in results of
%	the algorithm compared to the previous existing energies. Furthermore,
%	we propose a pipeline for its application in morphing,}
%
%\onecolumn \maketitle \normalsize \vfill
\setcounter{page}{3}
\input{sections/titlepage}
\thispagestyle{empty}

\thispagestyle{empty}
\chapter*{Acknowledgments}
\thispagestyle{empty}
I would like to sincerely thank my supervisors Oriol Pujol and Santi Segui for their support, guidance and mentorship. I greatly appreciate their demanding and inquisitive scientific attitude, while keeping always a calm and positive mindset. They are, in my mind, an inspiring example of what university professors should be.

Furthermore I would also like to dedicate this master thesis to my beloved parents and sister for their unsparing supports. My gratitude knows no bounds.

 Another special acknowledgment must be made to my friends in the master: Denis, Jeroni, Philipp, Pablo, Lorenzo, Iosu, Ferran and many others for the endless studying hours, morning coffees after crunching the brutal assignments all night long, valuable and constructive discussions which allowed me carry out this program. 
 



\pagenumbering{arabic}
\setcounter{page}{0}
\clearpage

%Table of contents
\newpage
\pagenumbering{roman} % Roman numerals
\chapter*{Abstract}
\thispagestyle{empty}
The main purpose of this master thesis is to enhance the performance of Cage Active Contours (CAC) in the context of color image object segmentation as well as provide a theoretical framework on which to justify the potential applications of the segmentation produced. 

We present two new energy functions which expand on the previous energies in CAC, by using Mixture Gaussian Models to capture multiple components per region, and extend their applicability to two different color spaces: RGB and the Hue component of HSI/HSV. Furthermore, we provide a mathematical formalization of the components in CAC (\textit{cage} and \textit{contour}) in order to demonstrate and prove the good properties that allow for a segmentation to be used for shape description and for image morphing and warping. In addition, we provide a public implementation in Python for object segmentation of CAC with different energies along with tools for image morphing and warping.

In order to validate our improvements, both quantitative and qualitative tests are used on three different datasets. The results show that the energy in RGB produces a substantial improvement over the previously developed energies for CAC. On the other hand we observe that the energy in the Hue component performs poorly on the given datasets despite its robustness with respect to changes in illumination. In the theoretical part, we prove which initial conditions are needed for a segmentation to provide useful results in shape description. Finally, we provide examples of some possible applications of CAC in morphing supported by our theoretical conclusions.

\tableofcontents

\listoffigures


\newpage
\pagenumbering{arabic} % Normal numerals

\newpage\null\thispagestyle{empty}\newpage
\input{sections/introduction}

\input{sections/related_work}

\input{sections/related_work}

\input{sections/proposed_methods}

\input{sections/implementation}

\input{sections/experiments}

\input{sections/applications}

\input{sections/conclusions}

\vfill
\renewcommand{\bibname}{\refname} % To change the heading of the chapter from Bibliography to References
\addcontentsline{toc}{chapter}{\bibname}

\bibliographystyle{apalike}

\bibliography{example.bib}

%\section*{\uppercase{Appendix}}
%
%\noindent If any, the appendix should appear directly after the
%references without numbering, and not on a new page. To do so please use the following command:
%\textit{$\backslash$section*\{APPENDIX\}}

\vfill
\end{document}